Time Series Bootstrapping For Solar Current

### 2021-12-14 deliverables/paper.Rmd
Preprocessing section

>>>>

# Preprocessing

To translate raw irradiance data into meaningful current data, several steps had to be taken to simulate the electrical workings of a real PV module. First, adjustments had to be made to account for the fact that an imperfect amount of irradiance actually reaches a PV module for capture. Then, effective irradiance must be translated into output current and maximized with an attached power processor. The process and accompanying assumptions are given below.

## Effective Irradiance

The effective irradiance that reaches a PV module is different from the total irradiance emitted by the sun due to a variety of small considerations that must be made. Among these are the tilt and rotation of the Earth, the latitude and longitude of the PV module, and the inclination of the panel towards the horizon. Most simply, $I_{eff} \propto I_{sun} cos \theta(t, N)$ where $\theta \in [-\frac{\pi}{2},\frac{\pi}{2}]$ is the angle between the sunlight and the surface of the solar cell. 
$$
\begin{aligned}
cos \theta(t, N) = & sin \gamma(N) sin La cos \beta - \\
& sin \gamma(N) cos La sin \beta cos \alpha + \\
& cos \gamma(N) cos La cos \beta cos w(t,N) + \\
& cos \gamma(N) sin La sin \beta cos \alpha cos w(t,N) + \\
& cos \gamma(N) sin \beta sin \alpha sin w(t,N) \\
\end{aligned}
$$
Here, $\gamma (N) = sin^{-1}[sin(.409)sin(D(N))]$ is known as the declination angle and is calculated from the angle of the Earth's axis and a metric $D(N) = 360(N - 81)/360$ where $N \in [1, 365]$ is the day of the year. $La \in [0, \frac{\pi}{2}]$ is the latitude of the PV module in radians. $\alpha = .524$ corresponds to whether the panel faces East or West and $\beta = .785$ describes the angle between the panel and the horizon; these values were supplied as assumptions. Finally, the hour angle $w(t, N)$ accounts for the angle of sunlight given the rotation of the Earth. 
$$
\begin{aligned}
w(t,N) &= 15 (AST(t,N) - 12) \\
AST(t,N) &= t + \Delta t + ET(N) \\
&= t + \frac{Lo - 15 UTC_{off}}{15} + ET(N) \\
ET(N) &= [9.87sin(2D(N)) - 7.53cos(D(N)) - 1.5sin(D(N))] / 60
\end{aligned}
$$
Here, $AST(t,N) \in [0,24]$ is the apparent solar time relative to the sun and is calculated as an adjustment to the current time $t$ based on longitude $Lo$, an offset from the coordinated universal time $UTC_{off}$, and the equation of time $ET(N)$. The above calculations produce results in degrees but values were switched to radians before trigonometric functions were applied. Ultimately, $I_{eff} \propto I_{sun} cos \theta(t, N)$ resulted from our astronomical adjustments and was used for PV module calculations.

## PV Module

Within the PV module, effective irradiance is translated into output current but the entire process is regulated by an attached power processor that ensure that the maximum power is extracted. It does this by testing a range of open circuit voltages $v_{oc}$ between zero and an assumed maximum $v_{oc} = 1.8$ on the PV module's I-V curve which describes how current and voltage vary together for each solar cell in the module. Here, the I-V curve is given by 
$$
i_{out} = i_{l} - i_{o}[e^{\frac{qv}{n \kappa T}} - 1]
$$ 
with constants $q = 1.6*10^{-19}$ and $\kappa = 1.38 * 10^{-23}$. The light-generated current $i_{l}(t,N) = .0005 I_{eff}(t,N)$ which adjusts $I_{eff}$ for the assumed short circuit current $i_{sc} = 5$ and a radiation rate factor. With a leakage factor $i_{o}$ and the ambient temperature $T$ in degrees Kelvin, $i_{out}$ can be calculated for various voltage values. The combined power of the module is then calculated by 
$$
P = n_{p} n_{s} max\{i_{out} v\}
$$ 
where $n_{p} = 6$ is the assumed number of parallel-wired solar cells in the module and $n_{s} = 6$ is the assumed number of series-wired solar cells in the module. A final conversion efficiency factor $\eta = .211$ is applied and $P'_{max} = \eta P_{max}$ is returned.
